---
title: "Air quality analysis and the correlation of car  accident"
author: "Frank Zhang"
date: "October 30, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = T, warning = F, message = F, cache.lazy = FALSE)
```

## Data description
Air quality data collected at outdoor monitors across the United States, Puerto Rico, and the U.S. Virgin Islands. The data comes primarily from the AOS data base. (Among which we chose the data of Ozone and SO2.) The data is downloaded in
[Air_Quality](https://aqsdr1.epa.gov/aqsweb/aqstmp/airdata/download_files.html#Raw).


## Library used
```{r library}
library(ggplot2)
library(dplyr)
library(readr)
library(lubridate)
library(ggmap)
library(plotly)
library(shiny)
library(stringr)
```


# Load data

```{r, eval = T}
full_df <- read_csv("Ozone.csv")
dim(full_df)
full_df2<- read_csv("SO2.csv")
dim(full_df2)
full_dfn<- read.csv("accident.csv")
dim(full_dfn)
```

```{r, cache = T}
set.seed(123)
df<- sample_n(full_df, 10000)
df2<- sample_n(full_df2, 10000)
dfn<- sample_n(full_dfn, 10000)
```

```{r delete}
df2<- df2%>%
  mutate(df2one = 
           str_replace(`Method Name`,"INSTRUMENTAL - ", ""))
df2<- df2%>%
  mutate(df2_new = 
           str_replace(df2one,"Instrumental - ", ""))

df<- df%>%
  mutate(dfone = 
           str_replace(`Method Name`,"INSTRUMENTAL - ", ""))
df<- df%>%
  mutate(df_new = 
           str_replace(dfone,"Instrumental - ", ""))

```

# Understand the Data
```{r Number of Method}
#Overlook of Method used
df%>%
  group_by(`Method Name`)%>%
  summarise(n())
```

```{r Study of Method vs. Sample Measurement}
#See if there is difference between the data generated using different Method.
df%>%
  group_by(`Method Name`)%>%
  summarise(mean_measure = mean(`Sample Measurement`))
ggplot(df)+
  geom_boxplot(aes(x = df_new, y = `Sample Measurement`))+
  ggtitle("Sample Mesurement with Method Name")+
  theme(axis.text.x = element_text(angle = 22, hjust = 10))+
  theme(text = element_text(size=8))
ggplotly()
```

The data of sample measurement collected by different Method shows little difference. 

# Data analysis
```{r Time in Second to Time in Hour}
Ozone <- df%>%
  mutate(Time_in_Hour = `Time Local`/3600)
SO2 <- df2%>%
  mutate(Time_in_Hour1 = `Time Local`/3600)
```

## Time vs. Sample Measurement
```{r Ozone}
Ozone%>%
ggplot()+
  geom_boxplot(mapping = aes(x=factor(Time_in_Hour), y=`Sample Measurement`)) +
  ggtitle("Measure of Ozone with time for each Method")
ggplotly()
```